Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-27 lloveras_2020.tex
nueva figura3 y retoques

Using the high cadence of data available, one image every 10 minutes were used. The selected images were averaged in 6-hour intervals. Which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation. For both rotations, the first 14 days of data were used.

\diego{
Some technical improvements were applied in this work, a 3D regularization scheme was used instead of the latitude-longitude regularization scheme used in previous DEMT reconstructions. This implies that the results of the tomography are now more reliable at lower heights and limit-induced artifacts are minimized. For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization. This level is different for each wavelength band and is sensitive to}

@@

@@

\diego{
As a way of knowing the physical position of all traced lines, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all open and closed file lines traced in gray scale at $1.105\,\mrsun$ for both rotations, where the ARs where excluded. At top, all traced legs with enaugh tomographic data are shown. In black all legs corresponding to closed lines and in grey corresponding to open lines. This traced lines were divided into four types as explained in Section \ref{trace} and the fit in density and temperature was applied, selecting only those legs that met the criteria. The bottom figure shows the latitudinal-longitudinal location of this selected lines at same height. In blue the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down legs). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down legs in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. A decrease in the amount of down legs in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In red the type I lines, populating all the streamer but mostly the mid latitudes. In violet the type II lines, which are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.
}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

\diego{No son los mismos colores que el paper de ceci, tmb quizas podriamos poner la cant de LOOPS y los valores medianos, ceci insiste.}

>>>>

Using the high cadence of data available, one image every 10 minutes were used. The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation. For both rotations, the first 14 days of data were used.

\diego{ DONDE QUEDA MEJOR COMENTAR ESTA MEJORA?
Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}

@@

\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}

@@

As a way of knowing the physical position of all traced lines, Figure \ref{rpoint_demt} shows the latitudinal-longitudinal location of all open and closed file lines traced in gray scale at $1.105\,\mrsun$ for both rotations, where the ARs where excluded. At top, all traced legs with enaugh tomographic data are shown. In black all legs corresponding to closed lines and in grey corresponding to open lines. This traced lines were divided into four types as explained in Section \ref{trace} and the fit in density and temperature was applied, selecting only those legs that met the criteria. The bottom figure shows the latitudinal-longitudinal location of this selected lines at same height. In blue the type 0 lines are indicated, populating the most equatorial latitudes (dominated mostly by down legs). This kind of structures has been informed in previous works, \citet{lloveras_2017} observed down legs in a rotation during the solar minima of 1996 and for the previous rotation CR-2081. A decrease in the amount of down legs in equatorial latitudes could be an indicator of increased coronal activity \citet{nuevo_2013}. In red the type I lines, populating all the streamer but mostly the mid latitudes. In violet the type II lines, which are mostly very large trans-equatorial field lines forming the envelope of the Streamer belt, and in green dots the type III lines, populating the coronal holes.

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.\albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca. Doy dos ejemplos para no dejar dudas. Para $\NCB$ de Type-II: $1.0\,(-21\%)$. Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
\label{tabla_demt}
\end{table}

@@
